True versus apparent shapes of astrophysical bow shocks

### 2017-05-08 papers/Paper1/quadrics-bowshock.tex
Split the paper into two parts!
* The theoretical paper is now called quadrics-bowshock.tex
* The applications paper has the original name: proplyd-bowshock.tex
Incorporate appendix into both papers
incorporate appendix
Move appendices to after references
Automatically generate data for table of tail coefficients
This is done in Rc-revisited-2016.org in the section "Write LaTeX
version of the tail analytic fit for paper".  The results are then
pasted into the latex file.
Make a start on a new observations section for the paper
Describe bow shock tracing algorithm
Add a couple of \clearpage com

\RequirePackage{amsmath}
\documentclass[useAMS, usenatbib]{mnras}

@@

% Standard LaTeX packages
% \usepackage[varg]{txfonts}
\usepackage[varg]{newtxmath}
\usepackage{newtxtext}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{color}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

@@

%% Bundled custom packages
\usepackage{aastex-compat}
%\usepackage{astrojournals}

@@

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Tarango Yong \& Henney]{
  Jorge A. Tarango Yong \& William J. Henney\\
  \AddressCRyA
}
\begin{document}
\maketitle
\begin{abstract}
  We develop a general framework for the effects of viewing angle on
  the apparent shape of a limb-brightened, cylindrically symmetric
  curved shock (bow shock).  
\end{abstract}

\input{sec-intro}
\input{sec-generic-model}
\input{sec-projection}
\input{sec-conic}
\input{sec-application}
\input{sec-conclusions}

\bibliographystyle{mnras}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}

>>>>

%\RequirePackage{amsmath}
\documentclass[useAMS, usenatbib, a4paper]{mnras}
\pdfsuppresswarningpagegroup=1

@@

% Standard LaTeX packages
% \usepackage[varg]{txfonts}
\usepackage[varg]{newtxmath}
\usepackage{newtxtext}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{color}
\usepackage{enumerate}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{hyperref}

\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

\usepackage{etoolbox}
\robustify\bfseries
\robustify\itshape

@@

%% Bundled custom packages
\usepackage{aastex-compat}

% Definitions needed in abstract
\newcommand\hii{\ion{H}{ii}}

@@

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Tarango Yong \& Henney]{
  Jorge A. Tarango Yong \& William J. Henney\\
  \AddressCRyA
}
\begin{document}
\maketitle
\begin{abstract}
  Stellar bow shocks are the result of the supersonic interaction
  between a stellar wind and its environment.  Some of these are
  "runaways": high-velocity stars that have been ejected from a star
  cluster.  Others are "weather vanes", where it is the local
  interstellar medium itself that is moving, perhaps as the result of
  a champagne flow of ionized gas from a nearby \hii{} region.  We
  present a new two-dimensional classification scheme for the shape of
  such bow shocks, which accounts for both the apex (pointy versus
  flat) and the wings (open versus closed).  For different theoretical
  bow shock models, we show how variations in the true shape can be
  disentangled from projection effects due to variations in the
  inclination angle.  We apply our classification scheme to three
  different observational datasets: mid-infrared arcs around hot
  main-sequence stars (\(N = 227\)), far-infrared arcs around luminous
  cool stars (\(N = 7\)), and emission-line arcs around proplyds and other
  young stars in the Orion Nebula (\(N = 18\)).  We find significant
  differences between the three datasets: cool star bow shocks have
  markedly more closed wings than hot star bow shocks, while
  differences in the shape of the apex region are only marginally
  significant.  The Orion Nebula arcs, on the other hand, have both
  significantly more open wings and significantly flatter apices than
  the OhotB star bow shocks.  We discuss the implications of these
  differences for understanding the physics of the bow shock
  interaction in the three classes of sources.
\end{abstract}

\input{sec-intro}
\input{sec-generic-model}
\input{sec-projection}
\input{sec-conic}
\input{sec-thin-shell}
\clearpage
\input{sec-quadrics-observations}
\input{sec-conclusions}
\bibliographystyle{mnras}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}
\clearpage
\input{quadrics-appendix}
